---
title: "Introduction to Package binomial"
author: "Yusheng Xia"
date: "5/3/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Package binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
```

## Binomial Package

The package '"Binomial"' is a package that contains many functions that relate to the famous binomial probability distribution. The package contains five main functions:
  
  - bin_choose(n, k) to calculate the number of combinations in which *k* successes can occur in *n* trials.
  - bin_probability(k, n, p) to calculate the probability of getting *k* successes in *n* trials with a *p* success probability.
  - bin_distribution(n, p) to return a dataframe of class '"bindis"' that has number of successes (up to n) in first column and probability of success number in second.
  - bin_cumulative(n, p) to return a dataframe of class '"bincum"' that is the same as bin_distribution() but also contains a column of cumulative probability.
  - bin_var(n, p) to return a named list of class '"binvar"' that contains the number of trials *n* and probability of success *p*.
  
In addition, the package also contains various methods that allow for easy plotting and summary functions to be displayed to users.

## bin_choose()

The bin_choose(n, k) function allows a user to see the total number of possible combinations of getting *k* successes in *n* trials.

```{r}
#Possible combinations in 4 trials with 3 successes.
bin_choose(4, 3)
```

In order for bin_choose(n, k) to be successfully run, n must be a positive integer number while k must be a positive integer less than or equal to n.

## bin_probability()

The bin_probability(k, n, p) function allows a user to calculate the probability of getting *k* successes given *n* trials and probability *p* of a single success.

```{r}
#Proability of getting 4 successes in 5 trials with a probability 0.2 of success
bin_probability(4, 5, 0.2)
```

Bin_probability(k, n, p) has the same limitations on inputs *n* and *p* as on bin_choose(n, p), and the input *k* must be a integer greater than or equal to 0 that is also less than or equal to *n*.

## bin_distribution()

The bin_distribution(n, p) function returns a dataframe that contains two columns, one column that shows all possible successes leading to *n*, and another that has the probability of each possible success number with the probability of one success given by *p*.

```{r}
#Dataframe of possible successes in 5 trials and 0.3 success per trial.
bin_distribution(5, 0.3)
```

After creating the dataframe, users can call the method *plot* to plot a bargraph of the dataframe given that the dataframe is of class '"bindis"'.

```{r}
#Bar graph of possible successes and probability of possible successes in 5 trials with 0.3 success per trial.
dis1 <- bin_distribution(5, 0.3)
plot.bindis(dis1)
```

Just like the functions above it, bin_distribution(n, p) can only take an input *n* that is an integer greater than or equal to 0 and a probability *p* that is between 0 and 1.

## bin_cumulative()

The bin_cumulative(n, p) function returns a dataframe similar to that of bin_distribution, but has an additional column that shows the cumulative distribution given each additional success. Given the nature of probabilities, the cumulative probability leading up to *n* successes is 1. The dataframe output is of class '"bincum"'.

```{r}
#Dataframe with cumulative probability added.
bin_cumulative(5, 0.3)
```

After creating the dataframe, users can call on the method *plot* to plot a cumulative line graph of the dataframe given that the dataframe is of class '"bincum"'.

```{r}
#Cumulative line graph of possible successes and cumulative probability of successes in 5 trials with 0.3 success per trial.
dis2 <- bin_cumulative(5, 0.5)
plot.bincum(dis2)
```

Just like the functions above it, bin_cumulative(n, p) can only take an input *n* that is an integer greater than or equal to 0 and a probability *p* that is between 0 and 1.

## bin_variable()

The bin_variable(n, p) function that returns a named list that is of class '"binvar"' and has the number of trials and probability of success printed out to see.

```{r}
#Using bin_variable()
bin1 <- bin_variable(10, 0.3)
bin1
```

After using bin_variable to create the named list, users are able to call upon the method *summary* to show the key summary statistics regarding the binomial distribution for that particular number of trials and probability.

```{r}
#Summary statistics for n = 10 and p = 0.3
bin1 <- bin_variable(10, 0.3)
summary(bin1)
```

Just like the functions above it, bin_variablen, p) can only take an input *n* that is an integer greater than or equal to 0 and a probability *p* that is between 0 and 1.
